\documentclass{article}
\usepackage{anysize}
\marginsize{3cm}{3cm}{3cm}{3cm}

\begin{document}

Version 2015.megalan.en.0

\section{Regulations}
\subsection*{General rules and regulations LAN-party ``MegaLAN''}
\textbf{1. General}\\
1.1 Hereafter, ``the organisation committee'' will refer to the organisation 
committee of the LAN-party ``MegaLAN''. ``MegaLAN'' will 
hereafter refer to the LAN-party ``MegaLAN'' held 10, 11, 12 april 2015.\\
1.2 The organisation committee reserves its exclusive right to deny without 
explanation any person access to the LAN event or to revoke said access.\\
1.3 The organisation committee reserves its exclusive right to modify without 
explanation the foregoing and hereafter mentioned rules.\\
1.4 In the event that situations not covered by the rules mentioned in this 
document occur during the event, the organisation committee reserves its 
exclusive right to make autonomous decisions, agreed to by the undersigned. \\
1.5 At the start of the LAN-event, each attendee is required to hand over a 
signed copy of these regulations to the organisation committee.\\
\\
\textbf{2. Software and Hardware}\\
2.1 Attendees require explicit permission from the organisation committee when 
taking unusually large or extra equipment (including but not limited to 
television screens, servers and game consoles). \\
2.1a Attendees in doubt about rule 2.1 are suggested to contact the organisation 
committee about the matter at hand. \\
2.2 The organisation committee cannot be held liable if (personal) belongings of 
any attendee are stolen.\\
2.3 The organisation committee cannot be held liable if (personal) belongings of 
any attendee go missing.\\
2.4 The organisation committee cannot be held liable for damage to any 
(personal) belonging of any attendee.\\
2.5 The attendees responsible for damage, or damage by theft, to anyone’s 
personal belongings, properties of the organisation 
committee, or University property, will be billed for the damage caused.\\
2.6 In case of theft, damage, or loss of personal belongings, Cover’s 
properties, organisation committee property, or University property, we will 
inform the police.\\
2.7 We do not condone Illegal software. If illegal software is stored on any of 
your devices, you alone will be held responsible for the possible repercussions. 
This rule applies to all files on all devices present at the LAN event.\\
2.7a Such files may include (but are not limited to) images, video files, audio 
files or executables.\\
2.8 The organisation committee cannot be held responsible for any data on any 
storage medium.\\
2.9 It is strictly prohibited to incapacitate or sabotage equipment, facilities 
and services installed by the organisation committee both on-site and off-site. 
Attendees who violate this rule will be held liable for the damage caused.\\
2.9a Organisation committee equipment includes but is not limited to: network 
switches, backbones, internet gateways, storage servers and game servers.\\
2.9b Services installed by the organisation committee include but are not 
limited to: the registration website and/or the matchmaking website.\\
2.9c Means of sabotage and incapacitation may include (but are not limited to) a 
denial-of-service attack on equipment, unplugging critical wires, spreading a 
virus, or a brute-force attack on the site’s login form.\\
2.10 It is strictly prohibited to incapacitate or sabotage equipment of other 
attendees by means of damage done to either hardware or software. For some 
examples, see 2.9c. Attendees who violate this rule will be held liable for the 
damage caused.\\
2.11 It is strictly prohibited to use the network and internet connection made 
available by the organisation committee for illegal activities. Attendees who 
violate this rule may be held liable for the resulting fines and damages.\\
2.11a Traffic is logged and filtered. The logs are always accurate.\\
2.11b Attendees caught torrenting are pitted against other violators in a small
lecture room with blunt objects and kitchen utensils. Last man standing will be
sent home.\\
2.12 It is strictly prohibited to use the internet connection made available by 
the organisation committee for filesharing protocols due to bandwidth 
considerations and legal issues. Popular filesharing protocols include but are 
not limited to the BitTorrent protocol or the Usenet protocol.\\
2.13 It is strictly prohibited to move or modify equipment and facilities 
installed by the organisation committee. You may however plug and unplug your 
own wires from the outlets and sockets you were assigned to.\\
2.14 It is strictly prohibited to bring along (computer) speakers to the LAN 
event or otherwise contribute to ambient noise with amplified sound. Headphones, 
earplugs and related devices are allowed. \\
2.14a Speakers built into computers, monitors, laptops, and other devices are 
allowed but are to be kept muted.\\
2.15 If the organisation committee is to receive complaints about excessive 
noise levels, the owner of the source of the excessive noise levels will be held 
responsible. Audio equipment may be confiscated and will be returned near the 
end of the LAN event. Emphasising 2.4: we cannot be held responsible for any 
damage caused to the confiscated equipment.\\
2.16 It is strictly prohibited to connect anything other than computers, 
monitors, phone chargers, and the occasional light source to the power grid, due 
to the capacity of the power grid. \\
2.17 If a power outage is caused by violation of rule 2.16, the owner of the 
violating appliance will be held responsible.\\
2.18 The organisation committee cannot be held liable for loss of data. 
Attendees are advised to make backups.\\
2.19 The organisation committee does not guarantee an uninterrupted and/or safe 
supply of power.\\
2.20 The organisation committee cannot be held responsible for damage caused by 
loss of power, lightning strikes, or raging demigods.\\
\\
\textbf{3. Alcohol, Drugs and Smoking}\\
3.1 Attendees of the LAN event are prohibited to possess and/or consume any type 
of recreational drugs at the LAN event. \\
3.2 Alcohol consumption is allowed in moderation. In the event of excessive 
alcohol consumption we reserve the exclusive right to remove any individuals who 
violate the foregoing rule. The organisation committee will determine the 
moderateness of the alcohol consumption on a case-by-case basis. \\
3.3 In the event of drug-consumption as prohibited in 3.1, we will notify the 
police. \\
3.4 Smoking is prohibited in the location of the LAN event.\\
\\
\textbf{4. Miscellaneous}\\
4.1 The display and/or exchange of material that depicts erotic behaviour is 
prohibited. \\
4.2 It is allowed to bring along one’s own non-alcoholic beverages to the LAN event. \\
4.3 It is prohibited to bring along one’s own alcoholic beverages to the LAN event.
4.4 It is allowed to bring along one’s own food to the LAN event. \\
4.5 The consumption of food and/or beverages provided by study associations is allowed 
but needs (as is custom) to be registered with the means available.\\
4.6 The distribution of copyrighted material is prohibited, unless the 
material’s licence allows the work(s) to be shared and re-used. \\
4.7 It is allowed to bring along one’s own chair but within reason. The organisation
committee has the final say in this. \\
4.8 It is prohibited to bring along one’s pillows, blankets, or anything of that 
nature to sleep on or under at the LAN event. \\
\\
\textbf{5. Financial}\\
5.1 Fees and costs stated on the website may be subject to errors.\\
5.1a It is up to the organisation commitee to determine if fees and costs are
in error.\\
5.2 Admission fees are as stated by the Organisation Committee on the MegaLAN
webpage, with respect to 5.1.\\
5.3 Payment of admission fee is fulfilled by attendee during the LAN event.\\
5.4 Fees for drinks and consumptions are not included in the admission fee.\\
5.5 Fees for the dinner served by parties affiliated with the  organisation 
committee are not included in the admission fee.\\
5.6 All payments are conducted by means of direct debit. \\
5.7 Admission fees are determined by and used strictly to cover the expenses of 
the event. Such expenses may include but are not limited to: Fuel for food 
transport, electrical infrastructure, network infrastructure, dinner and tape.\\

\section{Compliance Statement}
I, the undersigned, hereby agree with the foregoing rules of the LAN-party 
``MegaLAN'', held 10, 11 and 12 april 2015.
\\
Date:\\
\\
Name:\\
\\
Signature:\\

\end{document}
